Methods and Results

### 2021-03-27 ms.Rmd
checking main excel data file to go through all notes listed and to have a check of studies and data pulled from these studies. Adding some code to explore data further. Also added code to load packages"
Updated phylogeny, data prep and fit some preliminary models

>>>>

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms)

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

  # Bring in and prune tree
       tree <- read.tree("./phylogeny/tree")
       tree$tip.label <- gsub("_", " ", tree$tip.label)
  phylogeny <- vcv(tree, corr=TRUE)

  # Summary statistics for the results
  inverts <- data %>% 
             mutate(insect = ifelse(class %in% c("Insecta", "Gastropoda", "Malacostraca", "Arachnida", "Clitellata (Phylum Annelida)",  "Secernentea (Phylum Nematoda)"), 1,0))

model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)

model <- rma.mv(lnRR ~ 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)

model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)

model <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

model <- rma.mv(lnRR ~ SSD_lnRR, V =  data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
robust(model, cluster = data$study)

model <- rma.mv(lnRR ~ Harm_type, V = data$v_lnRR, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
robust(model, cluster = data$study)

model <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
robust(model, cluster = data$study)

```

# Results

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%).
